Multiple testing with logical dependencies

### 2013-08-15 paper/draft.tex
clarified proof

\begin{proof}
  We show by that given $p_{r+k} < \alpha$ all $E \in \mathscr{L}_{r+k} =
  \{I \in \mathscr{L}: r+k \in I\}$ are rejected by the stepwise
  procedure. First, notice that for all $E$ such that $\min E = r+k$
  rejection follows immediately and if $\min E \leq r$ rejection
  follows by rejection of $H_i$ for $i \leq r$. It remains to be shown
  that the stepwise procedure also rejects $H_E$ for $r < \min E <
  r+k$.

  First we show by contradiction that some $k \leq t$ we have $i \in
  \sigma \{r+l,r+k\}$ for some $i \leq r$ and all $1 \leq l < k$.  We
  need to show that for all $s,t$, $k+1 < s < t \leq k+l$, follows
  $i_s \sim K \cup i_t$:

  Assume that there is an $l$ such that there is on $i \leq r$ with $i
  \in \sigma \{r+l,r+k\}$. Consequently for all $i \leq r$ $i \nsim
  \{r+l,r+k\}$. Since $M(\mathscr{H})$ has no loops or parallels also
  $r+l \nsim r+k$. Consequently, for any maximally independent set in
  $I \subset \{1,...,r\}$, $I \cup \{r+l, r+k\}$ is independent and
  has cardinality $\rho\{1,...,r\}+2$ which contradicts
  (\ref{eq:cond.hierarchical}).

  Above argument can be repeated for any set $J \cup r+k$ where $J
  \subseteq \{r+1,...,r+k-1\}$. Therefore, we have $i \in E$, $i \leq
  r$ for all exhaustive set containing $r+k$ with $r < \min E <
  r+k$. Rejection of these sets follows from rejection of $H_i$, $i
  \leq r$, which completes the proof. 
\end{proof}

>>>>

\begin{proof}
  We show that given $p_{r+k} \leq \alpha$ for some $1 \leq k \leq s$
  all exhaustive sets $E \in \mathscr{L}_{r+k} = \{E \in \mathscr{L}:
  r+k \in E\}$ are rejected by the stepwise procedure. It remains to
  be shown that the stepwise procedure also rejects $H_E$ for all
  exhaustive sets with $\min E < r+k$. Note that $\{E \in \mathscr{L}:
  \min E < r+k\} = \overline{\underline{E}}_1^r \cup
  \overline{\underline{E}}^{r+k-1}_{r+1}$ where
  $\overline{\underline{E}}^b_a := \{\sigma I: \text{for all } I
  \subseteq S, a \leq \min I \leq b\}$. For $ E \in
  \overline{\underline{E}}_1^r$ follows since $p_i \leq \alpha$ for $i
  \leq r$.

  We show by contradiction that we have $i \in \sigma \{r+l,r+k\}$ for
  some $i \leq r$ and all $1 \leq l < k$.  Assume that there is an $l$
  such that there is no $i \leq r$ with $i \in \sigma
  \{r+l,r+k\}$. Consequently for all $i \leq r$, we have $i \nsim
  \{r+l,r+k\}$. Since $M(\mathscr{H})$ has no loops or parallels also
  $(r+l) \nsim (r+k)$. Consequently, for any maximally independent set
  $I \subset \{1,...,r\}$, $I \cup \{r+l, r+k\}$ is independent and
  has cardinality $\rho\{1,...,r\}+2$ which contradicts
  (\ref{eq:cond.hierarchical}).

  Above argument can be repeated for any set $I$ with $r+1 \leq \min I
  < k$. Therefore, we have $i \in E$ for all $E \in
  \overline{\underline{E}}^{r+k-1}_{r+1}$. Rejection of these sets
  follows from rejection of $H_i$, $i \leq r$, which completes the
  proof. 
\end{proof}
